---
title: "TITLE TK"
author: "Zoya Azhar, Ruby Wu, Ruth Tekleab Mekbib"
date: "April 8, 2019"
output:
  html_document:
    code_folding: hide
---

MacLeish has approximately four miles of built trail for use by field station visitors. We would like to be able to classify these trails as “Easy,” “Moderate,” or “Difficult” based on their length and change in elevation. Use the spatial data to develop a heuristic that will classify these (or any other) trails based on their difficulty. You might want to consult existing trail rating systems. It would be cool if you could create elevation profiles (e.g., this one).
Supporting data includes:
Existing trails shapefile
10’ contour elevation data


```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(macleish)
library(sf)
library(leaflet)
```

#classify trails as Easy, Moderate or Difficult
#based on length and total change in elevation
#time to walk


```{r message=FALSE, warning=FALSE, fig = 20}

# compute lengths for trails

lengths <- macleish_layers %>%
  pluck("trails") %>%
  st_length()

# create dataframe with lengths and get rid of non-trails

trails <- macleish_layers[["trails"]] %>%
  mutate(lengths = lengths) %>%
  filter(color != "") %>%
  filter(color != "Road")

# one trail's color was missing (as assigned by the official Macleish trail map)
  
trails$color <- as.character(trails$color)
trails[7,2] = "Green"
trails$color <- as.factor(trails$color)


# create dataframe with sum of lengths and total elevation change

# contains lengths 

initial <- trails %>%
  st_intersection(pluck(macleish_layers,"contours_3m")) %>%
  group_by(color,lengths) %>%
  summarise(segments = n(), elev_change = (max(ELEV_M)-min(ELEV_M)))

# contains total elevation change and total length of each trail

initial2 <- initial %>%
  group_by(color) %>%
  summarise(total_length = sum(lengths), elev_change = sum(elev_change), segments = sum(segments))

# can compute difficulty level using sqrt((elevation_gain)*2*(distance)), Shenandoah rating

final <- initial2 %>%
  mutate(difficulty = sqrt(as.numeric(((elev_change) *2* (total_length))))) %>%
  arrange(difficulty)

# plot 

ggplot() + 
  geom_sf(data = macleish_layers[["trails"]], color = "black") + 
  geom_sf(data = macleish_layers[["contours_3m"]]) +
  geom_sf(data = final, aes(color = color)) + #NEED TO DO scaleManual AND GET CORRECT COLORS
  geom_sf_label(data = final, aes(label = elev_change))

# contains elevation change at every intersection point

segment_intersection <- trails %>%
  st_intersection(pluck(macleish_layers,"contours_3m")) %>%
  arrange(color) %>%
  mutate(elev_change = ELEV_M-lag(ELEV_M))

# plot elevation change on each trail

change_at_pts <- ggplot(segment_intersection,aes(x = ELEV_M, y = elev_change)) +
  geom_line() +
  facet_wrap(~color)
change_at_pts


  
  

  

#my_plot <- leaflet() %>%
  #addTiles %>%
  #addMarkers(data = final)


#final2 <- final %>%
  #group_by(color) %>%
  #summarise(do_union = FALSE) %>%
  #st_cast("LINESTRING") %>%
  #ggplot(aes(color = color)) +
  #geom_sf()

#trails2 <- final %>% 
  #st_cast("MULTIPOINT") %>% 
  #st_cast("POINT")

#my_plot <- leaflet() %>%
  #addTiles() %>%
  #addPolylines(data = final2)

#my_plot

#base_plot <- leaflet() %>%
  #addTiles() %>%
  #addPolylines(data = macleish_layers[["trails"]], popup = ~ color)
#base_plot


blue <- trails %>%
  st_intersection(pluck(macleish_layers,"contours_3m")) %>%
  filter(color == "Blue") %>%
  arrange(color) %>%
  mutate(elev_change = ELEV_M-lag(ELEV_M))

ggplot() + 
  geom_sf(data = macleish_layers[["trails"]], color = "black") + 
  geom_sf(data = macleish_layers[["contours_3m"]]) +
  geom_sf(data = blue, color = "blue") +
  geom_sf_label(data = blue, aes(label = elev_change)) 

red <- trails %>%
  st_intersection(pluck(macleish_layers,"contours_3m")) %>%
  filter(color == "Red") %>%
  arrange(color) %>%
  mutate(elev_change = ELEV_M-lag(ELEV_M))

ggplot() + 
  geom_sf(data = macleish_layers[["trails"]], color = "black") + 
  geom_sf(data = macleish_layers[["contours_3m"]]) +
  geom_sf(data = red, color = "Red") +
  geom_sf_label(data = red, aes(label = elev_change))


# LABEL THEM ON MAP
# HOW TO GGREPEL ELEV_CHANGE LABELS ON MAP
# WANT A MAP WITH TRAILS HIGHLIGHTED AND RANKED, AND DIFFERENT POINTS OVER WHICH YOU CAN HOVER AND GET ELEV_CHANGE



```



```{r eval=FALSE}
# creating leaflet map

trails2 <- trails %>% 
  st_cast("MULTIPOINT") %>% 
  st_cast("POINT")

blue <- trails %>%
  st_intersection(pluck(macleish_layers,"contours_3m")) %>%
  filter(color == "Blue") %>%
  arrange(color) %>%
  mutate(elev_change = ELEV_M-lag(ELEV_M)) %>%
  st_cast("MULTIPOINT") %>% 
  st_cast("POINT")

diff_ranking <- final %>%
  
  
  

base_plot <- leaflet() %>%
  addTiles() %>%
  addPolylines(data = trails, layerId = ) %>%
  base_plot


%>%
  addPopups(data = blue)

  




# contains total length per trail
#total_lengths <- trails %>% 
  #group_by(color) %>%
  #summarise(sum(lengths))

# contains total length + elev_M
#length_elev <- total_lengths %>%
  #st_intersection(pluck(macleish_layers,"contours_3m"))

# contains total elevation change per trail
#elev_change <- length_elev %>%
  #group_by(color) %>%
  #summarise(N = n(), total_elev_change = (max(ELEV_M)-min(ELEV_M)))


```

```{r eval=FALSE}
# CREATE DATAFRAMES FOR EACH TRAIL WITH LENGTH AND ELEVATION CHANGE PER SEGMENT

segment_intersection <- trails %>%
  st_intersection(pluck(macleish_layers,"contours_3m")) %>%
  arrange(color) %>%
  mutate(elev_change = ELEV_M-lag(ELEV_M))
  

#each chunk has length per segment and elevation per segment
blue <- trails %>%
  st_intersection(pluck(macleish_layers,"contours_3m")) %>%
  filter(color == "Blue") %>%
  arrange(color) %>%
  mutate(elev_change = ELEV_M-lag(ELEV_M)) %>%
  st_cast("MULTIPOINT") %>% 
  st_cast("POINT")

blue_plot <- leaflet() %>%
  addTiles() %>%
  addPolylines(data = blue$geometry, 
               weight = 1, color = "blue",
               popup = ~ color)

Green <- trails %>%
  st_intersection(pluck(macleish_layers,"contours_3m")) %>%
  filter(color == "Green") %>%
  arrange(color) %>%
  mutate(elev_change = ELEV_M-lag(ELEV_M))

Red <- trails %>%
  st_intersection(pluck(macleish_layers,"contours_3m")) %>%
  filter(color == "Red") %>%
  arrange(color) %>%
  mutate(elev_change = ELEV_M-lag(ELEV_M))

White <- trails %>%
  st_intersection(pluck(macleish_layers,"contours_3m")) %>%
  filter(color == "White") %>%
  arrange(color) %>%
  mutate(elev_change = ELEV_M-lag(ELEV_M))

Yellow <- trails %>%
  st_intersection(pluck(macleish_layers,"contours_3m")) %>%
  filter(color == "Yellow") %>%
  arrange(color) %>%
  mutate(elev_change = ELEV_M-lag(ELEV_M))
  

```  

